### 2024-10-17 response/response.tex

The authors warmly thank the referees for their careful reading and numerous insightful comments. We consider each of them below.

\section{Report X}

\begin{verbatim}
a question out of curiosity: is there an explicit formula (in each case, and 
also for the associahedron) for a direction under which the poset is increasing, 
for the given geometric realization? (if there is an answer it could be 
mentioned)
\end{verbatim}

Done. We have added the explicit direction in the first paragraph of Section 2.4.

@@

\begin{verbatim}
bottom p2 "describe the geometry", should it not be "provide an explicit 
geometric realization" ? (since the geometric realization is not unique)
\end{verbatim}

Done. It was indeed unclear.

\begin{verbatim}
p3 the recursive definition of "above" is not ideal. Maybe cut it into 
defining "directly above" and then "above" (recursively using "directly 
above")
\end{verbatim}

Done. We unrolled the recursion with the sentence ``there is a sequence~${r = r_0, \dots, r_k = s}$ of rectangles such that the bottom edge of~$r_{i-1}$ lies in the same segment as the top edge of~$r_i$ for all~$i \in [k]$''.

@@

\begin{verbatim}
p4 when citing Figure 6 it could be mentioned (e.g. in a footnote) that 
even if for n=4 the strong rectangulotope is the permutohedron 
(combinatorially), the geometric realization is not the same (I am not 
very familiar with quotientopes but am a bit amazed by this fact, is it 
that if you remove deletable hyperplanes from the geometric realization 
of the permutohedron you would have a geometric realization of the strong 
rectangulotope with more involved vertex coordinates ?)
\end{verbatim}

Done. We have added the following sentence: ``Note that, contrarily to what could suggest this $n = 4$ case, the strong rectangulation lattice is not isomorphic to the weak order, and the strong rectangulotope is not combinatorially equivalent to the permutahedron as soon as~$n > 4$.''

@@

\begin{verbatim}
p7 Figure 7 caption, you should mention if it is for weak of strong 
(or both), and what the gray areas mean
\end{verbatim}

Done. We have added ``strong'' in the caption of Figure 7. We believe that the second sentence of the caption of Figure 7 explains the meaning of the grey areas. We also slightly modified the last paragraph of page 4 to be more precise on the definitions of the weak and strong rectangulation flip graphs.

@@

\begin{verbatim}
p10 first paragraph of 1.6: definition of the small inline symbol, the text 
seems to allow for the top edge of r_i to be aligned with the top edge of 
r_j, and bottom edge of r_i to be aligned with bottom edge of r_j, which 
is not what the drawing suggests
\end{verbatim}

Done. We slightly modified the symbols to avoid this problem.

\begin{verbatim}
For theorem 3 you could comment on what quantities in the vertex coordinates 
formula depends on the strong type and not just on the weak type (it seems 
to be only the Iverson bracket?)
\end{verbatim}

Done. We added a the sentence ``Note that the common leaves of~$T(R)$ and~$S(R)$ only depend on the weak class of the rectangulation~$R$'' after the definition of common leaves.

@@

\begin{verbatim}
p12 second line of paragraph starting with "An arc...", b should be b' in 
"a'\leq a<b\leq b" 
\end{verbatim}

Done.

\begin{verbatim}
p12 "It has a ray" is a bit vague, maybe give more visual intuition on what 
is a ray (is it a codimension 1 cone? or a union of some?)
\end{verbatim}

Done. A ray is a dimension~$1$ cone. We have modified the sentence just after to explain it properly.

@@

\begin{verbatim}
p13 l11 the remark "(in other words, if it is above..." may be too early 
(not sure it follows from something explained before)
\end{verbatim}

Done. We have delayed this observation to Remark 10.

\begin{verbatim}
p15 "bijection between the facets" -> "bijection between the facets of 
dimension 1" (?) also at the end of Section 4.2
\end{verbatim}

Our sentence is correct as the facets of a cone are its codimension~$1$ faces.

@@

\begin{verbatim}
p16 it could be good to give a short proof for Lemma 6 (e.g. explain which 
translate)
\end{verbatim}

Done. We added the explicit translation vector in Lemmas 6, 7, and 17.

@@

\begin{verbatim}
p20 Lemma 20 in the first bullet: "and vertical" should be deleted
\end{verbatim}

Done.

\begin{verbatim}
p21 two lines before Lemma 21 (announcing Lemma 21) you write "which do 
not have any associated yin arc", but this does not appear anymore in the 
statement of Lemma 21 (I do not see well how it relates)
\end{verbatim}

Done. We have reformulated the last two sentences of the paragraph to make the argument clearer.

@@

\begin{verbatim}
p21 in the proof of Lemma 21 "the right edge of r_i can not be on the 
right of the left edge of r_j" I wonder if it is well defined (it may 
depend on the geometric realization of the strong rectangulation)
\end{verbatim}

Todo.

\begin{verbatim}
after Lemma 21, I am not sure Lemmas 20 and 21 are enough to give the 
first part of Theorem 3, this would be the case if \prec_s was a total order. 
The case of pairs i,j not comparable in the strong order may also have to be 
covered in Lemma 21
\end{verbatim}

Done. You are right, it was incorrect. We replaced $i \prec_s^R j$ by $i \not\succ_s^R j$ in the hypothesis of Lemma 22. This is actually what the proof shows.

@@

\begin{verbatim}
Page 4:

"The strong rectangulation congruence... Its classes are in bijection with 
strong rectangulations.  The corresponding quotientopes will be referred 
to as the strong rectangulotopes and denoted by SR(n). Strong rectangulotopes 
can be obtained as quotientopes [PS19, PPR23] for the strong rectangulation 
congruence."

The last sentence seems to just repeat what has already been 
said earlier in the paragraph (except that it adds important references).  
Perhaps this paragraph can be revised.
\end{verbatim}

Done. We reformulated the last sentence to ``They can be obtained from the constructions of [PS19, PPR23]''.

@@

Some readers may appreciate a sentence defining the logical not symbol 
that you use (perhaps in the sentence after defining the Iverson bracket.
\end{verbatim}

Done. Just before Theorem~3.

\begin{verbatim}
In Theorem 3, there needs to be more clarification on "consecutive intervals".  
At first glance, I wasn't even sure whether that was a description of each 
interval separately or a description of the pair of intervals.  And then it 
wasn't clear whether they could be consecutive in either order or if I is always 
smaller.  After looking deeper into the paper, I conclude that you mean that 
the smallest element of J is one more than the largest element of I.  But you 
should say that explicitly somewhere (or correct my misunderstanding), 
probably right before the statement of Theorem 3.
\end{verbatim}

Done. We have decided to do it directly inside Theorem~3. The meaning is really that $\max(I) = \min(J)-1$.

@@

Done.

\begin{verbatim}
Page 12:

"It has a chamber for each permutation sigma of [n], given by the set of vectors 
whose coordinates are ordered as sigma."  It's a little unclear what you mean 
here, but as a "public service", it might be worth being very clear and pointing 
out to make these regions to match the vertices of the permutohedron in such 
a way that the edges are *right* weak order cover relations.  (As you know, 
it's *not* the obvious thing, "make the entries of sigma into a vector and 
let sigma label the region that contains that vector", but everyone assumes 
it is.)  Probably you could say something useful in far fewer words than I 
just used.
\end{verbatim}

Done. You are right. We replaced our unclear sentence by a formula: ``It has a chamber $\{\boldsymbol{x} \in \mathbb{R}^n \,|\, x_{\sigma_1} \le \dots \le x_{\sigma_n}\}$ for each permutation~$\sigma$ of~$[n]$''.
